UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-11 files/paper/paper.tex
update

\author{\IEEEauthorblockN{Cameron Fabbri}
\IEEEauthorblockA{Information Directorate\\
Air Force Research Laboratory \\
Rome, NY, USA.\\
cameron.fabbri@us.af.mil}
\and
\IEEEauthorblockN{Md Jahidul Muslim}
\IEEEauthorblockA{UMN\\}
\and
\IEEEauthorblockN{Junaed Sattar}
\IEEEauthorblockA{UMN\\
}}

@@

\subsection{Network Architecture and Training Details}
Our generator network uses an encoder-decoder structure similar to the work of \cite{isola2016image}, which is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
this embedding is then upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using
a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
generator uses kernel size $4 \times 4$ with stride 2. Following \cite{radford2015unsupervised}, we use batch
normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.

>>>>

\author{\IEEEauthorblockN{Cameron Fabbri}
\IEEEauthorblockA{Information Directorate\\
Air Force Research Laboratory \\
Rome, NY, USA.\\
cameron.fabbri@us.af.mil}
\and
\IEEEauthorblockN{Md Jahidul Islam}
\IEEEauthorblockA{UMN\\}
\and
\IEEEauthorblockN{Junaed Sattar}
\IEEEauthorblockA{UMN\\
}}

@@

\subsection{Network Architecture and Training Details}
Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
this embedding is then upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using
a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
by a leaky ReLU activation with slope $0.02$, while transpose convolutions in the encoder are followed by a ReLU
activation \cite{nair2010rectified}. Excempt from this is the last layer of the decoder, which uses a TanH nonlinearity
to match the input distribution of $[-1, 1]$. Following \cite{radford2015unsupervised}, we use batch normalization
\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.
